---
author: "John Nguyen"
date: "02/26/2022"
title: "Assignment 3: Data Visualization"
output: html_document
---

```{r, setup, include = FALSE}
library("tidyverse")
library("knitr")
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "../source")
```

```{r, sources, include = FALSE}
source("analysis.R")
source("trend.R")
```

# Report
<b>Proportion of Population is Asian American/Pacific Islander:</b>

## Introduction
Being of asian descent and living in washington state all my life I am curious 
about how the proportion of jail population differs for Asian Americans/Pacific
Islanders and Blacks in Washington State. To answer my questions, I will analyze
the incarceration dataset; mainly looking at: total population per county, 
total Black and AAPI population per county, total jail population per county,
and Black and AAPI jail population. 

## Summary
```{r, summary, echo = FALSE}
avg_aapi_prop <- average_aapi_prop(washington_data)
avg_black_prop <- average_black_prop(washington_data)
avg_aapi_jail_prop <- average_aapi_jail_prop(washington_data)
avg_black_jail_prop <- average_black_jail_prop(washington_data)
highest_black_jail_prop <- highest_black_jail_prop(washington_data)
highest_aapi_jail_prop <- highest_aapi_jail_prop(washington_data)
```
<b>Average Proportion of Total Population being Asian American/Pacific Islander 
vs Black (Per County in Washington State)</b><br>
<b>AAPI:</b> `r avg_aapi_prop`<br>
<b>Black:</b> `r avg_black_prop`<br>

<b>Average Proportion of Jail Population being Asian American/Pacific Islander 
vs Black (Per County in Washington State)</b><br>
<b>AAPI: </b> `r avg_aapi_jail_prop`<br>
<b>Black:</b> `r avg_black_jail_prop`<br>

<b>Highest Proportion of Jail Proportion being Asian American/Pacific Islander 
vs Black (Per County in Washington State)</b><br>
<b>AAPI: </b> `r highest_aapi_jail_prop`<br>
<b>Black: </b> `r highest_black_jail_prop`<br>

## Trends
```{r, trends, echo = FALSE}
filtered_data <- filter_data(data) 
generate_plot_black_pop(filtered_data)
```

This chart allows us to easily see the change in Black and 
Asian/Pacific Islander jail populations in King County over time. 
From the visual, we can see that the Black jail population is much greater and
grows more rapidly than the Asian/Pacific Islander jail population. Looking at 
spread in the data, it seems that the Asian/Pacific Islander jail population is
growing at a more steady rate whereas the Black jail population increases and
decreases more sporadically.

## Chart


## Map