---
author: "John Nguyen"
date: "02/26/2022"
title: "Assignment 3: Data Visualization"
output: html_document
---

```{r, setup, include = FALSE}
library("tidyverse")
library("knitr")
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "../source")
```

```{r, sources, include = FALSE}
source("analysis.R")
source("trend.R")
source("chart.R")
```

# Report
<b>Proportion of Population is Asian American/Pacific Islander:</b>

## Introduction
Being of asian descent and living in washington state all my life I am curious 
about how the proportion of jail population differs for Asian Americans/Pacific
Islanders and Blacks in Washington State. To answer my questions, I will analyze
the incarceration dataset; mainly looking at: total population per county 
between the age of 15 to 64, total Black and AAPI population per county, 
total jail population per county, and Black and AAPI jail population. 

## Summary
```{r, summary, echo = FALSE}
avg_aapi_prop <- average_aapi_prop(washington_data)
avg_black_prop <- average_black_prop(washington_data)
avg_aapi_jail_prop <- average_aapi_jail_prop(washington_data)
avg_black_jail_prop <- average_black_jail_prop(washington_data)
highest_black_jail_prop <- highest_black_jail_prop(washington_data)
highest_aapi_jail_prop <- highest_aapi_jail_prop(washington_data)
```
<b>Average Proportion of Total Population being Asian American/Pacific Islander 
vs Black (Per County in Washington State)</b><br>
<b>AAPI:</b> `r avg_aapi_prop`<br>
<b>Black:</b> `r avg_black_prop`<br>

<b>Average Proportion of Jail Population being Asian American/Pacific Islander 
vs Black (Per County in Washington State)</b><br>
<b>AAPI: </b> `r avg_aapi_jail_prop`<br>
<b>Black:</b> `r avg_black_jail_prop`<br>

<b>Highest Proportion of Jail Proportion being Asian American/Pacific Islander 
vs Black (Per County in Washington State)</b><br>
<b>AAPI: </b> `r highest_aapi_jail_prop`<br>
<b>Black: </b> `r highest_black_jail_prop`<br>

## Trends
```{r, trends, echo = FALSE}
jail_pop_data <- filter_jail_pop(data) 
generate_plot_black_pop(jail_pop_data)
```

This chart allows us to easily see the change in Black and 
Asian/Pacific Islander jail populations in King County over time. 
From the visual, we can see that the Black jail population is much greater and
grows more rapidly than the Asian/Pacific Islander jail population. Looking at 
spread in the data, it seems that the Asian/Pacific Islander jail population is
growing at a more steady rate whereas the Black jail population increases and
decreases more sporadically.

## Chart
```{r, comparison, echo = FALSE}
comparison_data <- comparison(data)
generate_comparison_plot(comparison_data)
```

From the previous visualization, I was able to see that the black jail
population was increasing over time. Due to knowing this fact, I became curious
as to whether or not the black jail proportion was increasing over time. Another 
factor that has been increasing over the years was the black population. I 
wanted to see whether or not there was a correlation between the growth of the 
black population and the growth of the black jail proportion. Based on the 
visual, there seems to be a negative correlation between the black jail
proportion and the black population. As one increases the other decreases. 

## Map
