---
author: "John Nguyen"
date: "02/26/2022"
title: "Assignment 3: Data Visualization"
output: html_document
---

```{r, setup, include = FALSE}
library("tidyverse")
library("knitr")
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "../source")
```

```{r, sources, include = FALSE}
source("analysis.R")
```

# Report
<b>Proportion of Population is Asian American/Pacific Islander:</b>

## Introduction
I grew up in a very protected environment. I was taught that being Asian meant that I had to behave, be respectful, and be smarter than those around me. I was also taught that certain ethnic groups should be avoided, such as blacks, since they are believed to be thieves and criminals. Now that I am older, I am starting to question the values that I have been taught since I was young. That is why I am curious about how the jail population proportions could differ for Asian Americans/Pacific Islanders and African Americans in Washington State.

## Summary
```{r, summary, echo = FALSE}
avg_aapi_prop <- average_aapi_prop(washington_data)
avg_black_prop <- average_black_prop(washington_data)
avg_aapi_jail_prop <- average_aapi_jail_prop(washington_data)
avg_black_jail_prop <- average_black_jail_prop(washington_data)
highest_black_jail_prop <- highest_black_jail_prop(washington_data)
highest_aapi_jail_prop <- highest_aapi_jail_prop(washington_data)
```
<b>Average Proportion of Total Population being Asian American/Pacific Islander vs Black (Washington State)</b><br>
<b>AAPI:</b> `r avg_aapi_prop`<br>
<b>Black:</b> `r avg_black_prop`<br>

<b>Average Proportion of Jail Population being Asian American/Pacific Islander vs Black (Washington State)</b><br>
<b>AAPI: </b> `r avg_aapi_jail_prop`<br>
<b>Black:</b> `r avg_black_jail_prop`<br>

<b>Highest Proportion of Jail Proportion being Asian American/Pacific Islander vs Black (Washington State)</b><br>
<b>AAPI: </b> `r highest_aapi_jail_prop`<br>
<b>Black: </b> `r highest_black_jail_prop`<br>

## Trends

## Chart

## Map